LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-11-09 main.tex
Correct equation references in ocean demo section

\begin{sloppypar}
In the geostrophic approximation, the sea-surface height $\eta$ serves as a stream-function for surface velocities. In a longitude-latitude $(\varphi,\theta)$ coordinate system, the evolution of a fluid particle is given by
\begin{eqnarray}
\pd{\varphi(\varphi,\theta,t)}{t} = -\frac{g}{R^2 f(\theta) \cos\theta} \pd{\eta(\varphi,\theta,t)}{\theta}\label{eq:dtlon}\\
\pd{\theta(\varphi,\theta,t)}{t} = \frac{g}{R^2 f(\theta) \cos\theta}\pd{\eta(\varphi,\theta,t)}{\varphi}
\label{eq:dtlat}
\end{eqnarray}
where $g$ is the constant of gravity, $R$ is the mean radius of the Earth, and $f(\theta) \equiv 2\Omega\sin\theta$ is the Coriolis parameter, with $\Omega$ denoting the Earth's mean angular velocity.
\end{sloppypar}

>>>>

\begin{sloppypar}
In the geostrophic approximation, the sea-surface height $\eta$ serves as a stream-function for surface velocities. In a longitude-latitude $(\varphi,\theta)$ coordinate system, the evolution of a fluid particle is given by
\begin{gather}
\pd{\varphi(\varphi,\theta,t)}{t} = -\frac{g}{R^2 f(\theta) \cos\theta} \pd{\eta(\varphi,\theta,t)}{\theta}\label{eq:dtlon}\\
\pd{\theta(\varphi,\theta,t)}{t} = \frac{g}{R^2 f(\theta) \cos\theta}\pd{\eta(\varphi,\theta,t)}{\varphi}
\label{eq:dtlat}
\end{gather}
where $g$ is the constant of gravity, $R$ is the mean radius of the Earth, and $f(\theta) \equiv 2\Omega\sin\theta$ is the Coriolis parameter, with $\Omega$ denoting the Earth's mean angular velocity.
\end{sloppypar}
